---
title: "Alcohol vs Seat choice"
author: "Juliet Clark"
date: "July 25, 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```

# Introduction

Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
you choose to sit in?

The data came from UC Davis.

$H_0$: There is no difference between the average number of drinks consumer and the row which people sit in.

$H_A$: There is a difference between number of drinks and row for at least two rows.

# Methods :

In the data set davisdata, seat is a categorical variable and alcohol is a numerical variable. 

We try to predict alcohol ~ seat so we use the numerical cat

# Results

## Descriptive Results

### Graphical Summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
This box plot shows that the further from the front one is. the higher values we get for alcohol consumption.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat, data=davisdata)
summary.aov(model1)
```

The p-value of this anova test is 0.000116 which is less than 0.5 therefore we reject the null hypothesis. 

## When significant follow up with TukeyHSD

```{r}
plot(TukeyHSD(model1))
```

From the middle to front there is no statistical difference in alcohol consumption. There is a difference in alcohol consumption from the front and back rows and also between the middle and back rows. 

## Conclusions

Due to the p-value (0.000116) being less than 0.05, we reject the null hypothesis and therefore know that alcohol consumption is dependent on the row someone may choose to sit in. 
